Notebook: Predictors of frog survival following translocation

### 2022-06-07 doc/notebook/notebook_translocation.Rmd
Minor edits to fix typos, add Results header

## Next steps
* Frog size had a marginally important effect on frog survival. Given association between frog size and donor varibles, create a second model that includes only donor = 72996. Given that there is considerable variation in frog sizes translocated from this site, this might allow an assessment of the effect of frog size independent of any effect of donor.  
* To assess within-site association between survival for the first and subsequent translocated cohorts, build another dataset that includes all recipient sites for which > 1 translocation was conducted. Include survival from the first translocation as the response variable and survival from the subsequent translocations as a predictor variable. Other predictors could also be included.

>>>>

## Results
* Important predictor variables in all models are relatively consistent (see `translocation_analysis_survival.Rmd` for details).

## Next steps
* Frog size had a marginally important effect on frog survival. Given association between frog size and donor variables, create a second model that includes only donor = 72996. Given that there is considerable variation in frog sizes translocated from this site, this might allow an assessment of the effect of frog size independent of any effect of donor.  
* To assess within-site association between survival for the first and subsequent translocated cohorts, build another dataset that includes all recipient sites for which > 1 translocation was conducted. Include survival from the first translocation as the response variable and survival from the subsequent translocations as a predictor variable. Other predictors could also be included (e.g., year).
